% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------
\documentclass[12pt,leqno]{article}

\usepackage[margin=1in]{geometry} 
\usepackage[fleqn]{amsmath}
\usepackage{amsthm,amssymb} 
%\usepackage{mathtools}
\usepackage{changepage} 
\usepackage{datetime} 
\usepackage{graphicx} 
\usepackage{color}
\usepackage{framed}

% logic proofs
\usepackage{lplfitch}
\usepackage{stmaryrd}

% images
\usepackage{subfigure} 
\usepackage{float} 
\usepackage{pdflscape} 
\usepackage{array}

\newcommand{\N}{\mathbb{N}} 
\newcommand{\Z}{\mathbb{Z}}

\usepackage{fancyhdr} 

% multiline box in align
\usepackage{tikz}
\newcounter{markeq}
\setcounter{markeq}{0}

\newcommand{\pstrut}[1]{\vrule height0pt depth0pt width0pt #1 \fboxsep}
\newcommand*\bmarkeq{\stepcounter{markeq}%
  \tikz[remember picture]\node(startframe-\themarkeq){\pstrut{height}};%
  \kern\fboxsep}
\newcommand*\emarkeq{\kern\fboxsep
  \begin{tikzpicture}[remember picture,overlay]
    \node (endframe-\themarkeq){\pstrut{depth}};
    \draw[,red,opacity=0.8] (startframe-\themarkeq.north) 
      rectangle (endframe-\themarkeq.south);
  \end{tikzpicture}%
}

% for headers/footer
\usepackage{lastpage}


\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------
\title{Mandatory Assignment 2} 
\author{Anders Fog Bunzel, 20112293\\ Mark Medum Bundgaard, 20112423\\Mikkel Brun Jakobsen, 20114457}

\maketitle

\headheight = 15pt
\thispagestyle{fancy} 
\pagestyle{fancy} \lhead{
\date{\today}} \chead{Introduction to Interactive 3D Graphics} \rhead{Group $<$AMM$>$} \cfoot{\thepage\ of 
\pageref{LastPage}}

\section{Representation of graphical elements}

\subsection{Blocks}
Our world consists of 40 by 30 blocks of 20 by 20 pixels.
Each block is represented as two triangles.
Each vertex has a position and a color attribute. The color is chosen based on the block type.
The buffer object containing block data is updated with (potentially new) data every frame. With this solution, deleting and creating new blocks is straightforward.

Block-data only needs to be updated interactively when it actually changes. With our current approach we update all blocks no matter what.

We could have used gl.bufferSubData.

Instead of representing the entire world in a single buffer, we could have partitioned it into multiple "chunks" and only update chunks that change.

\subsection{Block-outline}
We create a buffer containing 4 vertices once and for all.
The block-outline is drawn using the LINE\_LOOP mode.
In order to draw the block-outline at the desired position, we use a uniform to offset it.

\subsection{Stickman}
We create a buffer containing 10 vertices once and for all.
The Stickman is drawn using the LINES mode.
In order to draw the Stickman at the desired position, we use a uniform to offset it.

\section{Shaders}
All our positions are in "block space". Each of our vertex shaders converts block-space to clip-space coordinates.

Our Stickman/block-outline fragment shaders simply outputs a "hardcoded" color. The block fragment shader is augmented with the clickwave effect and a gradient based on a fragments distance to the center of the block it belongs to.

\subsection{ClickWave}
When the user places or destroys a block we start a "click wave". 

We implemented the click wave by displacing vertices away from the outline of a circle.

We can configure the center/radius of the circle from Javascript using uniforms.

We pass on the result of the calculation from the vertex shader to the fragment shader and use it to slightly darken fragments close to the outline of the circle.

\section{Browsers}

Our solution runs on Chrome and Firefox. For some reason gl.lineWidth(5) does not seem to have any effect on 1 out of 3 of our machines.

\section{Collision Detection}

Note: Our collision detection is far from perfect. 

% --------------------------------------------------------------
%     You don't have to mess with anything below this line.
% --------------------------------------------------------------
\end{document}










